### 2012-12-04 inst/examples/policycosts/policycosts.Rmd
use price=10 for better scaling

```{r}
profit <- profit_harvest(price = price, c0 = c0, c1 = c1)
c2 <- exp(seq(0, log(21), length.out = 20))-1
```

@@

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) c2 * h / x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

>>>>

```{r}
profit <- profit_harvest(price = price, c0 = c0, c1 = c1)
c2 <- exp(seq(0, log(price), length.out = 32))-1
```

@@

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) ( c2 * h / x) / price
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````
